---
title: "Data view of the Mental Health Study"
output: html_notebook
---

Load packages:

```{r}
library(foreign)
library(psych)
library(car)
library(stringr)
library(ggplot2)
library(likert) 
```

Load the data:

```{r}
dat <- read.csv("/home/cornelius/Documents/sustainability/mental_health/data_protected/preprocessed_data_v0.csv")
```

------------------------------------------------------------------------

# Section SD: Sociodemografics

#### [SD01] Gender "Which gender do you identify with?"

      0 = female; 
      1 = male; 
      NA = diverse, rather not say or Not answered

```{r}
table(dat$SD01, useNA='always' )
```

#### SD02 [age] "How old are you?" SD02_01 I am ... years old

    24: 24 and younger
    ..: age
    34: 34 and older

```{r}
table(dat$age,useNA='always' )
```

#### [SD08] Nationality "What is your nationality?"

-   europe: 1=Europe 0=Non-Europe
-   german: 1=German, 0=Non-German

```{r}
table(dat$europe, deparse.level = 2, useNA = "always")
table(dat$german, deparse.level = 2, useNA = "always")
```

#### [SD10] Family education background "What is your family's academic background?"

      1 = academic (at least one parent/legal guardian has a university degree)
      0 = non-academic (none of my parents/legal guardians has a university degree)
      NA = Not answered

```{r}
table(dat$SD10, useNA = "always")
```

#### [SD11] Formale Bildung (einfach) "Did you move to T?bingen for your Ph.D.?"

      0 = no
      1 = yes, from another place in Germany
      2 = yes, from another country
      NA = Not answered
      

```{r}
table(dat$SD11, deparse.level = 2, useNA = "always")
```

#### [SD13] Care-taking "Do you have a child/a person in your family you have to take care of?"

      0 = no
      1 = yes, from another place in Germany
      NA = Not answered

```{r}
table(dat$SD13, deparse.level = 2, useNA = "always")
```

#### SD14 [living] Living-arrangement "What is your housing situation?" (MC)

      1: Alone
      2: Together with parents / Together with partner / Together with family
      3: Student accommodation / Shared flat
      NA: not answered

```{r}
table(dat$living, deparse.level = 2, useNA = "always")
```

------------------------------------------------------------------------

# Section AP: About your PhD

#### [AP01] Faculty "Which faculty are your studies associated with?"

    1 = Science  
    2 = Economic and Social Sciences  
    3 = Humanities
    4 = Others (e.g. Theology, Medicine, Law)
    5 = Two faculties
    NA = not answered

```{r}
table(dat$faculty, useNA = "always")
```

#### [AP02] Choice of Topic "Did you choose the topic of your Ph.D. yourself?"

      0 = no
      1 = yes
      NA = Not answered

```{r}
table(dat$AP02, useNA = "always")
```

#### [AP03] Hours per week Ph.D "How many hours a week do you spend on your Ph.D.?"

        AP03_01 ... hours/week
        

```{r}
table(dat$AP03_01, useNA = "always")
```

#### [AP05] Hours per week work "How many hours a week do you work in total?"

-   AP05_01 ... hours/week
-   timedif: build difference between phd wporking hours and total working hours

```{r}
table(dat$AP05_01, useNA = "always")
```

```{r}
describe(dat$timedif)
```

#### AP04 [phdstage] Start Ph.D."When did you start your Ph.D.?"

-   phdstage: Time spent as a PhD

          1 = 0-6 months  
          2 = 7-12 months 
          3 = 13-18 months
          ...
          9 = 48-54 months
          10 = >54 months

```{r}
table(dat$phdstage,useNA = "always")
```

# Section EF: Employment/Financial Situation

#### [EF01] Contract Type "How are you financed? (Contract type only related to your Ph.D.)"

        1 = Permanent employment
        2 = Temporary employment
        3 = Hourly employment
        6 = Scholarship (employed, paying social security)
        7 = Scholarship (not employed)
        5 = Not employed
        8 = Others
        NA = Not answered
        Remark: if multiple matches in open answers: other

```{r}
table(dat$EF01, useNA = "always")
```

#### [EF02] Length of Contract "If you only have a temporary employment: What is the total length of your contract (in months)?"

        EF02_01 in months
        12: 0-12
        24: 13-24
        36: 25-36
        48: 37-48
        56: >48
      

```{r}

table(dat$EF02_01, useNA = "always")
```

#### [EF06] Length of scholarship "If you have a scholarship: What is the total length of your current scholarship (in months)?"

        EF06_01 in months
        24: 0-24
        36: 25-36
        48: >36

```{r}
table(dat$EF06_01, useNA = "always")
```

#### [EF03] % Full time "What is the percentage your contract covers in terms of full-time employment?"

        EF03_01 in %
        25: <=25
        50: 26-50
        60: 51-60
        70: 61-70
        80: 71-80
        100: 81-100

```{r}
table(dat$EF03_01)
```

#### [EF04] Other employment "Do you have any other paid employment which is unrelated to your Ph.D.?"

        0 = no
        1 = yes
        NA = Now answered 

```{r}
table(dat$EF04, useNA = "always")
```

#### [EF05] Reason other employment "Why did you decide to have a side-job?"

      ### EF05_01 Earning money/financial reasons
      ### EF05_02 For the CV
      ### EF05_03 Personal interest
      ### EF05_04 Other
      ### 0 = Not checked
      ### 1 = Checked

#### TODO #6

see open question procedure

```{r}
table(dat$EF05_01, useNA = 'always', dnn = 'EF05_01')
table(dat$EF05_02, useNA = 'always', dnn = 'EF05_02')
table(dat$EF05_03, useNA = 'always', dnn = 'EF05_03')
table(dat$EF05_04, useNA = 'always', dnn = 'EF05_04')
```

# Section EV: Evaluation of your Ph.D.

Summarizing scales:

  - Job satisfaction (JS): EV06, EV07, EV08 (Hellgren et al., 1997)
  
Single scales: 

-   scale in EV01, EV04, EV06, EV07, EV08

          1 = strongly disagree
          2 = disagree
          3 = neither agree nor disagree
          4 = agree
          5 = strongly agree
          -1 = not sure
          NA = Not answered

-   [EV01] PhD again "Looking back, if I had not started my Ph.D. yet, I would do it again."

-   [EV04] Regret "I regret having started a Ph.D."

Please evaluate in the scale the following statements regarding your Ph.D.:

-   [EV06] Job-satisfaction1 "I enjoy being at work."
-   [EV07] Job-satisfaction2 "I am content with the job I have."
-   [EV08] Job-satisfaction3 "I am satisfied with my job."

```{r}
table(dat$EV01, useNA = "always")
```

#### [EV09] Life-satisfaction "How satisfied are you with your life at the moment?"

        1 = not satisfied at all
        2 = slightly satisfied
        3 = moderately satisfied
        4 = very satisfied
        5 = totally satisfied
        NA = Not answered

```{r}
table(dat$EV09, useNA = "always")
```

#### [EV05] PhD somewhere else "Do you think doing your Ph.D. in/at a different country/university would offer better conditions?"

        0 = no; 
        1 = yes; 
        2 = not sure; 
        NA = Not answered
        

```{r}
table(dat$EV05, useNA = "always")
```

# Section WG: Structure of working group

#### [WG01] Professional support "Are there colleagues in your department/research center that support you professionally?"

        0 = no; 
        1 = yes;  
        NA = Not answered

```{r}
table(dat$WG01, useNA = 'always')
```

#### [WG02] Emotional support "Are there colleagues in your department/research center that support you emotionally?"

        0 = no; 
        1 = yes; 
        NA = Not answered

```{r}
table(dat$WG02, useNA = 'always')
```

# Section GH: General Health

Summarizing scale:

  - Perceived Stress Scale (PSS): GH01, GH02, GH03, GH04 (Cohen, 1984; Büssing, 2011) 
    (GH02 and GH03 are inverted for PSS)

Single scales:

-   scale in GH01, GH02, GH03, GH04

          1 = never
          2 = almost never
          3 = sometimes
          4 = fairly often
          5 = very often
          NA = Not answered

-   [GH01] Stress1 "...how often have you felt that you were unable to control the important things in your life?"

-   [GH02] Stress2 "...how often have you felt confident about your ability to handle your personal problems?"

-   [GH03] Stress3 "...how often have you felt that things were going your way?"

-   [GH04] Stress4 "...how often have you felt difficulties were piling up so high that you could not overcome them?"

```{r}
table(dat$GH01, useNA = "always")
```

# Section OR: Other responsibilities

#### [OR01] Reponsibilities besides PhD "What other responsibilities do you have besides working on your research topic/project?"

    ### OR01_01 Teaching
    ### OR01_02 Supervision of other students
    ### OR01_03 Administration
    ### OR01_04 Research unrelated to your topic
    ### OR01_08 Other, please specify
    ### OR01_09 No further responsibilities
    ### 0 = Not checked
    ### 1 = Checked

```{r}
table(dat$OR01_01, useNA = 'always', dnn = 'OR01_01')
table(dat$OR01_02, useNA = 'always', dnn = 'OR01_02')
table(dat$OR01_03, useNA = 'always', dnn = 'OR01_03')
table(dat$OR01_04, useNA = 'always', dnn = 'OR01_04')
table(dat$OR01_08, useNA = 'always', dnn = 'OR01_08')
table(dat$OR01_09, useNA = 'always', dnn = 'OR01_09')
```

#### [OR02] Time other responsibilities "How much time do you spend on other responsibilities besides your research activities?"

        OR02_01 ... %

```{r}
table(dat$OR02_01,useNA = 'always')
```

# Section ST: Stressors

Summarizing scales are:

  - Job insecurity (JI): ST13, ST14, ST15 (Hellgren et al., 1999)
  - Institutional Stressors (supervisor), positive wording (ISpositive): ST02,ST03,ST05,ST07
  - Institutional Stressors (supervisor), negative wording (ISnegative): ST01,ST04,ST06,ST08
  
Individual questions:

#### [ST01] Institutional-stressor1 "Have you ever felt looked down on by your supervisor?"

#### [ST02] Institutional-stressor2 "Do you feel supported by your supervisor?"

#### [ST03] Institutional-stressor3 "Do you feel your supervisor is interested in your topic?"

#### [ST04] Institutional-stressor4 "Have you ever felt mistreated (e.g., insulted, shouted at, undervalued) by your supervisor?"

#### [ST17] Institutional-stressor4_coll "Have you ever felt mistreated (e.g., insulted, shouted at, undervalued) by your colleagues?"

#### [ST05] Institutional-stressor5 "Does your supervisor encourage you to participate in career-building opportunities such as conferences, summer schools, research stays, etc.?"

#### [ST06] Institutional-stressor6 "Based on your experiences in academia so far, do you reconsider your career path?"

#### [ST07] Institutional-stressor7 "Do you feel comfortable contacting your supervisor when you need help?"

#### [ST08] Institutional-stressor8 "Has the behavior of your supervisor ever made you consider quitting your Ph.D.?"

#### [ST09] Institutional-stressor9 "Do you have regular meetings with your supervisor(s)?"

        Scale for [ST01] to [ST09] and [ST17]:
        1 = not at all
        2 = rarely
        3 = some of the time
        4 = most of the time
        5 = all of the time
        NA = Not answered

```{r}
table(dat$ST01, useNA = "always")
```

#### [ST16] Institutional-stressor10 "How often do you have meetings with your supervisor(s)?"

        1 = at least once a week
        2 = at least once a month
        3 = at least every three months
        4 = at least every six months
        5 = at least once a year
        6 = less than once a year
        NA = Not answered

```{r}
table(dat$ST16, useNA = 'always')
```

#### [ST11] Systemic-stressor1 "The lack of permanent/long-term contracts in academia worries me."

#### [ST12] Systemic-stressor2 I believe having a Ph.D. will help me to find a good job.""

#### [ST13] Job-insecurity1 "Please evaluate in the scale the following statements regarding your Ph.D.: “I am worried about having to leave my job before I would like to.”

#### [ST14] Job-insecurity2 "There is a risk that I will have to leave my present job in the year to come."

#### [ST15] Job-insecurity3 "I feel uneasy about losing my job in the near future."

        Scale for [ST11] to [ST15]
        1 = strongly disagree
        2 = disagree
        3 = neither agree nor disagree
        4 = agree
        5 = strongly agree
        NA = Not answered

```{r}
table(dat$ST11)
```

# Section MH: Mental Health

#### [MH01] Mental health 1 "How often do you feel stressed since you have started your Ph.D.?"

        1 = not at all
        2 = rarely
        3 = some of the time
        4 = most of the time
        5 = all of the time
        NA = Not answered

```{r}
table(dat$MH01, useNA = 'always')
```

#### [MH02] Mental health 2 "Has your stress level increased since you started your Ph.D.?"

        0 = No
        1 = Yes

```{r}
table(dat$MH02, useNA = 'always')
```

#### [MH03] Mental health 3 "What is/are the cause(s) of your stress?"

# [MH03_01]

# TODO #9: include open answer preprocessing

#### [MH04] Mental health 4 "Do you have anyone at your institute to consult about your work-related stress?" (MC)

        MH04_01 Nobody
        MH04_02 Colleagues
        MH04_03 Admins / Coordination
        MH04_04 Supervisor
        MH04_05 Other, please specify
        0 = Not checked
        1 = Checked
        MH04_05a Other, please specify (free text)

# TODO #10: open answer preprocessing

#### [MH05] Mental health 5 "Do you feel your mental health has declined due to the Ph.D.?"

        1 = not at all
        2 = somehow
        3 = plenty
        4 = severely
        NA = Not answered

```{r}
table(dat$MH05, useNA = 'always')
```

#### [MH06] Mental health 6 "What would need to change to improve your mental health status?"

        MH06_01 Free Text

# TODO #11: include open answer preprocessing

#### [MH07] Mental health 7 "Do you know other Ph.D. students who are struggling with their mental health?"

        1 = nobody
        2 = some
        3 = many
        4 = most
        5 = all
        NA = Not answered

```{r}
table(dat$MH07, useNA = 'always')
```

#### [MH08] Mental health 8 "Do you think your mental health problems negatively affect your quality of work?"

        1 = never
        2 = almost never
        3 = sometimes
        4 = fairly often
        5 = very often
        NA = Not answered

```{r}
table(dat$MH08, useNA = 'always')
```

#### [MH09] Mental health 9 "Do you think that some special services (e.g., time management courses, coaching, etc.) or structural changes are necessary?" (MC)

        MH09_01 no
        MH09_02 personalised coaching
        MH09_03 mentoring
        MH09_04 time management courses
        MH09_05 stress management courses
        MH09_08 structural changes
        MH09_09 Other, please specify
        0 = Not checked; 
        1 = Checked
        MH09_09a Other, please specify (free text)

# MH09_09a TODO #12: open answer

```{r}
table(dat$MH09_02)
```

#### [MH10] Psychotherapy "Are you currently in psychotherapy?"

        0 = no; 
        1 = yes; 
        NA = Not answered

```{r}
table(dat$MH10, useNA = 'always')
```

#### [MH11] Diagnosis "Have you ever been diagnosed with a mental disorder?"

        0 = no; 
        1 = yes; 
        NA = Not answered

```{r}
table(dat$MH11, useNA = 'always')
```

## PHQ2 and GAD7 

Summarizing scales are:

  - Perceived Health Questionaire (PHQ2): (MH12,MH14) (Bach et al.)
  - General Anxiety Disorder (GAD7): (MH15,MH16,MH17,MH18,MH19,MH20,MH21)  (Bach et al.)

Individual questions:

#### [MH12] PHQ_2\_1 "Little interest or pleasure in doing things"

#### [MH16] PHQ_9\_1 "Being so restless that it's hard to sit still"

#### [MH17] PHQ_9\_2 "Being tired easily"

#### [MH18] PHQ_9\_3 "Muscle tension or muscle pain"

#### [MH19] PHQ_9\_4 "Trouble falling asleep or sleeping through"

#### [MH20] PHQ_9\_5 "Trouble concentrating, e.g., on reading or watching TV"

#### [MH21] PHQ_9\_6 "Becoming easily annoyed or irritable"

#### [MH14] PHQ_2\_2 "Feeling down, depressed or hopeless"

        same scale for  'MH12', 'MH14','MH15','MH16','MH17','MH18','MH19','MH20','MH21'
        0 = Not at all
        1 = Several days
        2 = More than half the days
        3 = Nearly every day
        NA = Not answered

#### [MH15] PHQ_9\_Filter "Feeling nervous, anxious, or on edge?"

      scale for  [MH15] 
      0 = Not at all
      1 = Several days
      2 = More than half the days
      NA = Not answered

```{r}
table(dat$MH12, useNA = "always")
```

# Section SH: Seeking Help

#### [SH01] Seeking-help1 "Have you already tried to improve your situation?"

        1 = never
        2 = almost never
        3 = sometimes
        4 = fairly often
        5 = very often
        NA = Not answered

```{r}
table(dat$SH01, useNA = 'always')
```

#### [SH02] Seeking-help2 "Have you heard of the consultation services at the university?"

        0 = no; 
        1 = yes; 
        NA = Not answered

```{r}
table(dat$SH02, useNA = 'always')
```

#### [SH04] Seeking-help3 "How much do you know about the consultation services at the university?"

        1 = nothing
        2 = almost nothing
        3 = something
        4 = plenty
        5 = a lot
        NA = Not answered 

```{r}
table(dat$SH04, useNA = 'always')
```

#### [SH05] Seeking-help4 "Have you sought help from a specialist?"

        0 = no; 
        1 = yes; 
        NA = Not answered

```{r}
table(dat$SH05, useNA = 'always')
```

#### [SH10] Corona "Did the Covid-19 pandemic affect your general situation?"

        1 = yes, it improved my general situation
        2 = yes, it worsened my general situation
        3 = yes, but it neither worsened nor improved my general situation
        4 = no
        NA = Not answered

```{r}
table(dat$SH10, useNA = 'always')
```

#### [SH06] Seeking-help5 "Do you have anyone to talk to about your issues?"

        0 = no; 
        1 = yes; 
        NA = Not answered

```{r}
table(dat$SH06, useNA = 'always')
```

#### [SH07] Seeking-help6 "What could be done to improve your situation? Feel free to express your opinion and feelings here."

        SH07_01 [01] Free text

# todo #13 : open question

#### [SH09]Seeking-help7 "Do you have any further comments?"

        SH09_01 [01] Free text

# todo #14 : open question

#### [SH11] Corona2 "Do you think the answers you have provided in this survey have been affected by the Covid-19 pandemic?"

        1 = Very likely
        2 = Likely
        3 = Neutral
        4 = Not likely
        5 = Very unlikely
        NA = Not answered

```{r}
table(dat$SH11, useNA = 'always')
```

# Section CO: Informed consent

#### [CO05] Consent: Residual option (negative) or number of selected options

CO05_01 I have been informed about the study and the procedure. I hereby agree to the collection and processing of my above-mentioned data. Consequently, I would like to voluntarily participate in this study. 0 = Not checked; 1 = Checked

```{r}
table(dat$CO05, useNA = 'always')
```

#### [CO07] ConfirmationPHD: Residual option (negative) or number of selected options

CO07_01 I hereby confirm, that I am a Ph.D. student at the University of T?bingen. 0 = Not checked; 1 = Checked

```{r}
table(dat$CO07_01, useNA = 'always')
```

############################### END
